Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-03-07 manuscript.Rmd
materials section

Infants were recruited in one of two age groups: Younger infants were 4-7 months and older infants were 11-14 months. Families were recruited through social media advertisements and from community events in Southern California. There were `r num_younger` infants in the 4-7 month group (X female) and `r num_older` in the 11-14 month group (X female). Only 1 of session was excluded due to a technical error---one of the four IMU sensors failed to record, resulting in an unusable recording. The ethnicity for infants was reported as X Hispanix/Latinx and X for not Hispanix/Latinx. Race was reported as X Caucasian, X Asian, X ~~~ and X others. Parents were compensated \$30 in cash for each visit they completed. The BLINDED Institutional Review Board reviewed and approved all procedures associated with the study. All participants gave their informed consent to participate.
<!-- TODO RACE ETHNICITY SEX -->

Most participants were tested in a single session (`r nrow(num_sessions %>% filter(n == 1))`), but `r nrow(num_sessions %>% filter(n > 1))` participants contributed between 2-4 sessions as part of an ongoing longitudinal study. Across the two age groups, we report data on a total of `r length(unique(ppts$id_uni))` sessions, with `r num_sessions %>% filter(group == "Younger") %>% pull(n) %>% sum` from younger infants and `r num_sessions %>% filter(group == "Older") %>% pull(n) %>% sum` from older infants. Across sessions, younger infants' age ranged from `r age["Younger","min"]` to `r age["Younger","max"]` (*M* = `r age["Younger","mean"]`) and older infants' age ranged from `r age["Older","min"]` to `r age["Older","max"]` (*M* = `r age["Older","mean"]`).

@@

>>>>

Infants were recruited in one of two age groups: *Younger* infants were between 4 and 7 months and *Older* infants were between 11 and 14 months. There were `r num_younger` infants in the 4-7 month group (X female) and `r num_older` in the 11-14 month group (X female). Families were recruited through social media advertisements and from community events in Southern California. The ethnicity for infants was reported as X Hispanix/Latinx and X for not Hispanix/Latinx. Race was reported as X Caucasian, X Asian, X ~~~ and X others. Parents were compensated \$30 in cash for each visit they completed. The BLINDED Institutional Review Board reviewed and approved all procedures associated with the study. All participants gave their informed consent to participate.
<!-- TODO RACE ETHNICITY SEX, COUNT BY HAND -->

Most participants were tested in a single session (*n* = `r nrow(num_sessions %>% filter(n == 1))`), but `r nrow(num_sessions %>% filter(n > 1))` participants contributed between 2-4 sessions as part of an ongoing longitudinal study. Only 1 session was excluded due to a technical error---one of the four IMU sensors failed to record, resulting in an unusable set of data for classification. Across the two age groups, we report data on a total of `r length(unique(ppts$id_uni))` sessions, with `r num_sessions %>% filter(group == "Younger") %>% pull(n) %>% sum` sessions from younger infants and `r num_sessions %>% filter(group == "Older") %>% pull(n) %>% sum` sessions from older infants. Across sessions, younger infants' age ranged from `r age["Younger","min"]` to `r age["Younger","max"]` (*M* = `r age["Younger","mean"]`) and older infants' age ranged from `r age["Older","min"]` to `r age["Older","max"]` (*M* = `r age["Older","mean"]`).

@@

Four inertial movement units (IMUs) were used to record infant movement across the day (MC10 Biostamp). A custom garment was made to hold the IMUs: Internal pockets were sewn into a snug-fitting pair of infant leggings so that IMUs would stay close to the body and so that infants could not pull out the sensors. On each side of the body there was a pocket over the hip and a pocket just above the ankle. Each sensor recorded accelerometer and gyroscope data at 62.5 Hz throughout the day, with sufficient battery and on-device storage to record for approximately 12 hours. Infants also wore a LENA&reg; recorder throughout the day in the front pocket of a LENA&reg; shirt, located near the infant’s chest.

Video recordings were captured using an action camera on a miniature tripod (Insta360 ONE R) that caregivers placed in the room that the infant was in. The proprietary "Boosted Battery Base" attached to the action camera to allow for a total of 3 hours of recording. However, as described below, this created two video files separated by a variable gap of approximately 40 s. Caregivers also received a log sheet to record times that infants napped as well as times that the sensor garment was removed from the infant (e.g., baths, diaper changes).

### 2023-03-07 manuscript.tex
materials section

Infants were recruited in one of two age groups: Younger infants were 4-7 months and older infants were 11-14 months. Families were recruited through social media advertisements and from community events in Southern California. There were 9 infants in the 4-7 month group (X female) and 14 in the 11-14 month group (X female). Only 1 of session was excluded due to a technical error---one of the four IMU sensors failed to record, resulting in an unusable recording. The ethnicity for infants was reported as X Hispanix/Latinx and X for not Hispanix/Latinx. Race was reported as X Caucasian, X Asian, X \textasciitilde\textasciitilde\textasciitilde{} and X others. Parents were compensated \$30 in cash for each visit they completed. The BLINDED Institutional Review Board reviewed and approved all procedures associated with the study. All participants gave their informed consent to participate.

Most participants were tested in a single session (17), but 6 participants contributed between 2-4 sessions as part of an ongoing longitudinal study. Across the two age groups, we report data on a total of 34 sessions, with 14 from younger infants and 20 from older infants. Across sessions, younger infants' age ranged from 3.84 to 7.16 (\emph{M} = 4.99) and older infants' age ranged from 10.74 to 14.23 (\emph{M} = 11.75).

@@

>>>>

Infants were recruited in one of two age groups: \emph{Younger} infants were between 4 and 7 months and \emph{Older} infants were between 11 and 14 months. There were 9 infants in the 4-7 month group (X female) and 14 in the 11-14 month group (X female). Families were recruited through social media advertisements and from community events in Southern California. The ethnicity for infants was reported as X Hispanix/Latinx and X for not Hispanix/Latinx. Race was reported as X Caucasian, X Asian, X \textasciitilde\textasciitilde\textasciitilde{} and X others. Parents were compensated \$30 in cash for each visit they completed. The BLINDED Institutional Review Board reviewed and approved all procedures associated with the study. All participants gave their informed consent to participate.

Most participants were tested in a single session (\emph{n} = 17), but 6 participants contributed between 2-4 sessions as part of an ongoing longitudinal study. Only 1 session was excluded due to a technical error---one of the four IMU sensors failed to record, resulting in an unusable set of data for classification. Across the two age groups, we report data on a total of 34 sessions, with 14 sessions from younger infants and 20 sessions from older infants. Across sessions, younger infants' age ranged from 3.84 to 7.16 (\emph{M} = 4.99) and older infants' age ranged from 10.74 to 14.23 (\emph{M} = 11.75).

@@

Four inertial movement units (IMUs) were used to record infant movement across the day (MC10 Biostamp). A custom garment was made to hold the IMUs: Internal pockets were sewn into a snug-fitting pair of infant leggings so that IMUs would stay close to the body and so that infants could not pull out the sensors. On each side of the body there was a pocket over the hip and a pocket just above the ankle. Each sensor recorded accelerometer and gyroscope data at 62.5 Hz throughout the day, with sufficient battery and on-device storage to record for approximately 12 hours. Infants also wore a LENA® recorder throughout the day in the front pocket of a LENA® shirt, located near the infant's chest.

Video recordings were captured using an action camera on a miniature tripod (Insta360 ONE R) that caregivers placed in the room that the infant was in. The proprietary ``Boosted Battery Base'' attached to the action camera to allow for a total of 3 hours of recording. However, as described below, this created two video files separated by a variable gap of approximately 40 s. Caregivers also received a log sheet to record times that infants napped as well as times that the sensor garment was removed from the infant (e.g., baths, diaper changes).
